True versus apparent shapes of astrophysical bow shocks

### 2016-05-09 papers/Paper1/sec-application.tex
Analysis of Rc completed

Now, to obtaining $R_c$ we expand  (\ref{eq:th1th}) until order 2nd order for small $\theta$ values to find that for such values
$\theta_1 = \beta^{1/2}\theta$

This expansion is valid when k is integer or multiple of 1/2.

Expanding equation (23) from \citep{Canto:1996} and substituting $\theta_1$ we found that:

\begin{align}
R \simeq R_0 \left(1+\frac{1+2\beta^{1/2}}{6}\theta^2\right)
\label{eq:R_approx}
\end{align}

@@

\begin{equation}
R_c = \frac{3}{2}R_0\left(1-\beta^{1/2}\right)^{-1}
\label{eq:Rcurv}
\end{equation}

>>>>

Now, to obtaining $R_c$ we expand  (\ref{eq:th1th}) until order 4th order for small $\theta$ values to find that for such values

\begin{align}
\theta_1^2 &\simeq \beta\theta^2\left[1+ \left(A_k-\frac{\beta}{15}\right)\theta^2\right] \\
\mathrm{where:~} & A_k = \frac{1}{15}-\frac{k}{20}
\end{align}
Expanding equation (23) from \citep{Canto:1996} and substituting $\theta_1$ we found that:

\begin{align}
R &\simeq R_0 \left(1+\gamma\theta^2\right)
\label{eq:R_approx}
\mathrm{where:~} & \gamma = \frac{1}{6} + \frac{\beta^{1/2}}{3}\left[1+\frac{1-\beta^{1/2}}{10}-\frac{3}{40}\frac{k}{1+\beta^{1/2}}\right]
\end{align}

@@

\begin{equation}
R_c = R_0\left(1-2\gamma\right)^{-1}
\label{eq:Rcurv}
\end{equation}
